\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis

### 2024-09-07 Paper/Paper.tex
add keywords
add table of content

	\title{\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis}
	\author{Siqi Pan}
	\date{}
	\maketitle

	\vspace{-0.2cm}
	\hrule
	\vspace{-0.1cm}
	\section*{Abstract}
	\hrule
	\vspace{0.4cm}
	We devise a novel model, the Multimodal Abnormity-Aware Model (MAAM), for assisting ocular disease diagnosis. The MAAM enables input of 2 kinds of ophthalmological images, namely optical coherence tomography (OCT) and color fundus images, and simulates the decision-making process by deducing the disease from abnormities. The model is composed of 2 submodels, the Abnormity Models and the Diagnosis Model, where the Abnormity Models identify 11 OCT abnormities and 8 fundus abnormities, and the Diagnosis Model identifies 12 diseases by integrating features from the former model. In MAAM, we introduce the fusion mechanism, the concept of codominant abnormities and diseases, and the Abnormity-to-Disease Criteria.  The model breaks the black box of complex neural network and expose more interpretable information for the reference of ophthalmologists. And it gets the overall accuracy of 89\% and thus the feasibility is verified.
	\vspace{0.4cm}
	\hrule
	\vspace{1cm}

@@

	\pagebreak
	\section*{Appendix}

>>>>

	\title{\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis}
	\vspace{-0.5cm}
	\author{Siqi Pan}
	\vspace{-0.5cm}
	\date{}
	\maketitle

	\vspace{-0.7cm}
	\hrule
	\vspace{-0.3cm}
	\section*{Abstract}
	\hrule
	\vspace{0.3cm}
	We devise a novel model, the Multimodal Abnormity-Aware Model (MAAM), for assisting ocular disease diagnosis. The MAAM enables input of 2 kinds of ophthalmological images, namely optical coherence tomography (OCT) and color fundus images, and simulates the decision-making process by deducing the disease from abnormities. The model is composed of 2 submodels, the Abnormity Models and the Diagnosis Model, where the Abnormity Models identify 11 OCT abnormities and 8 fundus abnormities, and the Diagnosis Model identifies 12 diseases by integrating features from the former model. In MAAM, we introduce the fusion mechanism, the concept of codominant abnormities and diseases, and the Abnormity-to-Disease Criteria.  The model breaks the black box of complex neural network and expose more interpretable information for the reference of ophthalmologists. And it gets the overall accuracy of 89\% and thus the feasibility is verified.

	\vspace{0.2cm}
	{\fontsize{12pt}{12pt}\selectfont \hspace{-0.8cm}\textbf{Keywords: }Multimodal, Deep Learning, Abnormity-Aware, Ocular Diagnosis}
	\vspace{0.3cm}
	\hrule

	\tableofcontents

@@

	\pagebreak
	\section*{Appendix}
	\addcontentsline{toc}{section}{Appendix}
